\mythesistitle

### 2011-11-20 src/synopsis.tex
- made some formatting changes in intro - committing before making the major v0.2 review changes.

\title{\mythesistitle} 
\author{\myname} 
\date{\MakeUppercase
  {\mysubmissionmonth}} 
\department{\MakeUppercase {\mydept}}

@@

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}
% \listoftables
% \addcontentsline{toc}{chapter}{LIST OF TABLES}
% \listoffigures
% \addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}

@@

\def \LLL {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
\def \GGG {{\em ``The String {\bf T}heory''}} 
\def \BBB {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}

\def \xLLL {{\bf B}}
\def \xGGG {{\bf T}} 
\def \xBBB {{\bf W}}
\def \xTTT {{\bf F}}

@@

@@

@@

Let $U$ and $\cF$ represent the set of students and the set of study
groups respectively and the integers $n$ and $m$ denote the total
number students and study groups respectively. In relation to this
example, these are defined as follows. Also given below is the study group
allocation to students. \tnote{use tables}
\tnote{use other font for elements of sets}
\begin{enumerate}[]
\item {$U = \{$Pa,$\; $Pi,$\; $Sn,$\; $Wo,$\; $Vi,$\; $Li,$\; $Ch,$\;
    $Sa,$\; $Fr,$\; $Sc,$\; $Lu$\}$}
\item $\cF = \{\xLLL, \xGGG, \xBBB, \xTTT\}$
\item $\xLLL = \{$ Ch,$\; $ Sa,$\; $ Fr,$\; $ Sc,$\; $ Lu $\}$
\item $\xGGG = \{$ Pa,$\; $ Pi,$\; $ Vi,$\; $ Ch $\}$
\item $\xBBB = \{$ Su,$\; $ Pi,$\; $ Wo $\}$
\item $\xTTT = \{$ Vi,$\; $ Li,$\; $ Ch,$\; $ Fr $\}$
\item $n = |U| = 11$, $m = |\cF| = 4$
\end{enumerate}

@@

An intuitive approach to this problem would be to first find the paths
that each study group decides to inhabit and then refine the
allocation to individual students. A feasible allocation of exclusive
routes to study groups is illustrated in Fig~\ref{fig:streetmappath}
and the students' allocation of apartments that obey's this route
allocation is shown in Fig~\ref{fig:streetmappathpeople}. How this is
algorithmically computed is the focus of this thesis.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.3]{../img/1_infinite_loop.png}
  \caption{{\residenceblock} street map}
  \label{fig:streetmap}
\end{figure}

\begin{figure}[h]
  \centering
%  \includegraphics[scale=0.5]{../img/2_infinite_loop.png}
  \includegraphics[scale=0.5]{../img/2_infinite_loop_BTWF.png}
  \caption{{\residenceblock} street map with study group routes
    allocated. Routes are color coded as follows: red for
    \textcolor{red}{\xLLL} group, blue for \textcolor{blue}{\xGGG}
    group, orange for \textcolor{YellowOrange}{\xBBB} group, green for
    \textcolor{green}{\xTTT} group}
  \label{fig:streetmappath}
\end{figure}

@@

If all the apartments are on the same street or if they are all lined
up on a single path, the street map becomes a tree that is just a
path. Then the problem becomes what is called an {\em interval
  assignment problem}. The idea of interval assignment may not be
obvious here; hence to see this, consider a different problem in
{\WSI} where the classes for these study groups courses need to be
scheduled during a day (or a week or any time period). Each study
group has a bunch of courses associated with it some of which may be
shared by two or more study groups. It is mandatory that a student who
is a member of a study group takes all the courses associated with
that group. There are slots during the day for classes to be held and
the problem is to allocate class slots to courses such that all the
classes of a study group are consecutive. It is debatable if this will
not hamper the attention span and memory retention rate of the students but
that is, regrettably, out of the scope of this thesis. The parallels between this
class allocation problem and the accommodation problem can be seen as
follows. The set $U$ here, are the courses offered (say Course 101 ``Post
modernism in Wallace's work'', Course 102 ``A study on fragmented prose
method'' and so on). The collection $\cF$ is the set of study groups but the
study groups are filled by course IDs and not students like in the
earlier example. For instance, Course 101 is mandatory for all study
groups {\bf L, G, B, T} and Course 102 is mandatory for only the {\bf B}
group) and so on. The sequence of class slots for the day (or week or
any time period) is analogous to the street map in the accommodation
problem. It is quite obvious now why this version of the problem
(where the ``target graph'' is a path and not any tree) is called an
interval assignment problem.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.4]{../img/0_cop_nocop.png}

@@

% \begin{figure}[h] 
%   \centering
%   (i) \includegraphics{cop-tree_thesis.1} \ \ \ \ \ \  
%   (ii)  \includegraphics{cop-tree_thesis.2}
%   \caption{(i) $8$-subdivided star with 7 rays, (ii) 3-subdivided
%     star with 3 rays}
%   \label{fig:kstar}
% \end{figure}

>>>>

\title{\mythesistitle} 
\author{\myname} 
\date{\MakeUppercase
  {\mysubmissionmonth}} 
\department{\MakeUppercase{\mydept}}

@@

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}
\listoftables
\addcontentsline{toc}{chapter}{LIST OF TABLES}
\listoffigures
\addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}

@@

% \def \LLL {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
% \def \GGG {{\em ``The String {\bf T}heory''}} 
% \def \BBB {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
% \def \TTT {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}
\def \LLL {{\em ``$\mathbb{B}$rief Interviews with Hideous Men''}}
\def \GGG {{\em ``The String $\mathbb{T}$heory''}} 
\def \BBB {{\em ``[$\mathbb{W}$]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``$\mathbb{F}$ate, Time, and Language: An Essay on Free Will''}}

% \def \xLLL {{\bf B}}
% \def \xGGG {{\bf T}} 
% \def \xBBB {{\bf W}}
% \def \xTTT {{\bf F}}
\def \xLLL {\mathbb{B}}
\def \xGGG {\mathbb{T}} 
\def \xBBB {\mathbb{W}}
\def \xTTT {\mathbb{F}}

@@

\def \xPa {{\bf Pa}} 
\def \xPi {{\bf Pi}} 
\def \xSn {{\bf Sn}}
\def \xWo {{\bf Wo}}
\def \xVi {{\bf Vi}} 
\def \xLi {{\bf Li}} 
\def \xCh {{\bf Ch}}
\def \xSa {{\bf Sa}}
\def \xFr {{\bf Fr}}
\def \xSc {{\bf Sc}} 
\def \xLu {{\bf Lu}}

@@

\def \coneohone {{\em ``Influence of post modernism in Wallace's work''}}
\def \coneohtwo {{\em ``A study on fragmented prose method''}}

@@

Let $U$ and $\cF$ represent the set of students and the set of study
groups respectively and the integers $n$ and $m$ denote the total
number students and study groups respectively. In relation to this
example, these are defined as follows. Also given below is the study group
allocation to students. \tnote{use tables}
\tnote{use other font for elements of sets}

% \vspace{-3mm}
% \begin{align*}
% U &= \{\xPa,\; \xPi,\; \xSn,\; \xWo,\; \xVi,\; \xLi,\; \xCh,\;
%     \xSa,\; \xFr,\; \xSc,\; \xLu\}\\
% \cF &= \{\xLLL, \xGGG, \xBBB, \xTTT\}\\
% \xLLL &= \{\xCh,\;  \xSa,\;  \xFr,\;  \xSc,\;  \xLu \}\\
% \xGGG &= \{\xPa,\;  \xPi,\;  \xVi,\;  \xCh \}\\
% \xBBB &= \{\xSn,\;  \xPi,\;  \xWo \}\\
% \xTTT &= \{\xVi,\;  \xLi,\;  \xCh,\;  \xFr \}\\
% n &= |U| = 11\\
% m &= |\cF| = 4  
% \end{align*}

\begin{table}[htbp]
  \centering
  \begin{tabular}{ll}
    $U $&$= \{\xPa,\; \xPi,\; \xSn,\; \xWo,\; \xVi,\; \xLi,\; \xCh,\;
    \xSa,\; \xFr,\; \xSc,\; \xLu\}$\\
    $\cF $&$= \{\xLLL, \xGGG, \xBBB, \xTTT\}$\\
    $\xLLL $&$= \{\xCh,\;  \xSa,\;  \xFr,\;  \xSc,\;  \xLu \}$\\
    $\xGGG $&$= \{\xPa,\;  \xPi,\;  \xVi,\;  \xCh \}$\\
    $\xBBB $&$= \{\xSn,\;  \xPi,\;  \xWo \}$\\
    $\xTTT $&$= \{\xVi,\;  \xLi,\;  \xCh,\;  \xFr \}$\\
    $n $&$= |U| = 11$\\
    $m $&$= |\cF| = 4$      
  \end{tabular}
  \caption{Students and study groups in \WSI}
  \label{tab:wsigroups}
\end{table}

@@

An intuitive approach to this problem would be to first find the paths
that each study group decides to inhabit and then refine the
allocation to individual students. A feasible allocation of exclusive
routes to study groups is illustrated in Fig~\ref{fig:streetmappath}
and the students' allocation of apartments that obeys this route
allocation is shown in Fig~\ref{fig:streetmappathpeople}. How this is
algorithmically computed is the focus of this thesis.

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.3]{../img/1_infinite_loop.png}
  \caption{{\residenceblock} street map}
  \label{fig:streetmap}
\end{figure}

\begin{figure}[htbp]
  \centering
%  \includegraphics[scale=0.5]{../img/2_infinite_loop.png}
  \includegraphics[scale=0.5]{../img/2_infinite_loop_BTWF.png}
  \caption{{\residenceblock} street map with study group routes
    allocated. Routes are color coded as follows: red for
    \textcolor{red}{$\xLLL$} group, blue for \textcolor{blue}{$\xGGG$}
    group, orange for \textcolor{YellowOrange}{$\xBBB$} group, green for
    \textcolor{green}{$\xTTT$} group}
  \label{fig:streetmappath}
\end{figure}

@@

As a special case, suppose all the apartments are on the same
street or if they are all lined up on a single path, the street map
becomes a tree that is just a path. Then the problem becomes what is
called an {\em interval assignment problem}. The idea of interval
assignment may not be obvious here; hence to see this, consider a
different problem in {\WSI} where the classes for these study groups
courses need to be scheduled during a day (or a week or any time
period). Each study group has a bunch of courses associated with it
some of which may be shared by two or more study groups. It is
mandatory that a student who is a member of a study group takes all
the courses associated with that group. There are slots during the day
for classes to be held and the problem is to allocate class slots to
courses such that all the classes of a study group are consecutive. It
is debatable if this will not hamper the attention span and memory
retention rate of the students but that is, regrettably, out of the
scope of this thesis. The parallels between this class allocation
problem and the accommodation problem can be seen as follows. The set
$U$ here, are the courses offered (say Course 101 {\coneohone}, Course
102 {\coneohtwo} and so on). In this variation of the problem, the
collection $\cF$ is the set of study groups but the study groups are
filled by course IDs (in place of students in the earlier
example). For instance, Course 101 is mandatory for all study groups
$\xLLL$, $\xGGG$, $\xBBB$, $\xTTT$ and Course 102 is mandatory for
only the $\xLLL$ group) and so on. The sequence of class slots for the
day (or week or any time period) is analogous to the street map in the
accommodation problem. It is quite obvious now why this version of the
problem (where the ``target graph'' is a path and not any
tree\tnote{\footnote{Allowing any tree in this example could be seen
    as a scenario where there are parallel classes. A node falling in
    the path between two other nodes would mean that the corresponding
    is scheduled between the other two.}}) is called an interval
assignment problem.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.4]{../img/0_cop_nocop.png}

@@

% \begin{figure}[htbp] 
%   \centering
%   (i) \includegraphics{cop-tree_thesis.1} \ \ \ \ \ \  
%   (ii)  \includegraphics{cop-tree_thesis.2}
%   \caption{(i) $8$-subdivided star with 7 rays, (ii) 3-subdivided
%     star with 3 rays}
%   \label{fig:kstar}
% \end{figure}
